Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-28 Documents/Paper/ms.tex
No MNRAS control sequence
Feroz paper
More talk

\section{Sinusoidal example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications, and has been solved analytically
under certain sets of assumptions \citep[see e.g.][]{bretthorst}.

@@

@@

\bibitem[Hobson 
\& McLachlan(2003)]{2003MNRAS.338..765H} Hobson, M.~P., \& McLachlan, C.\ 2003, \mnras, 338, 765

\bibitem[Irwin(1985)]{irwin} Irwin, M.~J.\ 1985, \mnras, 214,
575

>>>>

\section{Sinusoidal example}
In this section we demonstrate a seemingly simple example which exhibits
a phase transition, making a standard MCMC approach difficult. Suppose
a signal is composed of $N$ sinusoids, of different periods, amplitudes,
and phases. The signal is observed at various times $\{t_i\}_{i=1}^N$ with
noise, and we want to use the resulting data to infer the number of sinusoids
$N$, along with the periods $\{T_i\}_{i=1}^N$, amplitudes $\{A_i\}_{i=1}^N$,
and phases $\{\phi_i\}_{i=1}^N$.
This kind of model has many applications, and has been solved analytically
under certain sets of assumptions \citep[see e.g.][]{bretthorst}. Similar
models have been used in many different fields
\citep[e.g.][]{}. Note that this problem is also very closely related to the
problem of detecting exoplanet signals in radial velocity data, which has
attracted a lot of interest
\citep[e.g.][]{2007ApJ...654..551B, gregory, fengji, 2011MNRAS.415.3462F}.

@@

\bibitem[Feroz et al.(2011)]{2011MNRAS.415.3462F} Feroz, F., Balan, S.~T.,
Hobson, M.~P.\ 2011.\ Detecting extrasolar planets from stellar radial
velocities using Bayesian evidence.\ Monthly Notices of the Royal
Astronomical Society 415, 3462-3472.

@@

\bibitem[Gregory(2011)]{gregory} Gregory, P.~C.\ 2011.\ 
Bayesian exoplanet tests of a new method for MCMC sampling in highly 
correlated model parameter spaces.\ Monthly Notices of the Royal 
Astronomical Society 410, 94-110.

\bibitem[Hobson 
\& McLachlan(2003)]{2003MNRAS.338..765H} Hobson, M.~P., \& McLachlan, C.\ 2003, MNRAS, 338, 765

\bibitem[Hou et al.(2014)]{fengji} Hou, F., Goodman, J., Hogg, 
D.~W.\ 2014.\ The Probabilities of Orbital-Companion Models for Stellar 
Radial Velocity Data.\ ArXiv e-prints arXiv:1401.6128.

\bibitem[Irwin(1985)]{irwin} Irwin, M.~J.\ 1985, MNRAS, 214,
575
